---
title: "EHR UX/UI Mockup"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: embed
    theme:
        version: 4
        primary: "#2C3E50"
        navbar-bg: "#2C3E50"
    mathjax: null
---

```{r setup, include=FALSE}
library(flexdashboard)
library(htmltools)
library(summarywidget)
library(crosstalk)
library(tidyverse)
library(lubridate)
library(reactable)
library(reactablefmtr)
library(htmltools)
library(htmlwidgets)
library(d3scatter)
library(ggsci)
library(rmarkdown)

valueBoxSummaryWidget <- function (value, caption = NULL, icon = NULL, color = NULL, href = NULL) 
{
    if (!is.null(color) && color %in% c("primary", "info", 
        "success", "warning", "danger")) 
        color <- paste0("bg-", color)
    valueOutput <- tags$span(class = "value-summarywidget-output", `data-caption` = caption, 
        `data-icon` = icon, `data-color` = color, 
        `data-href` = href, value)
    hasPrefix <- function(x, prefix) {
        if (!is.null(x)) 
            grepl(paste0("^", prefix), x)
        else FALSE
    }
    fontAwesome <- hasPrefix(icon, "fa")
    ionicons <- hasPrefix(icon, "ion")
    deps <- flexdashboard:::html_dependencies_fonts(fontAwesome, ionicons)
    if (length(deps) > 0) 
        valueOutput <- attachDependencies(valueOutput, deps)
    valueOutput
}
```

```{r setup2, include = FALSE}
# Excel Read In
ehr_poc1 <- readxl::read_xlsx(
    "C:/Users/andyb/Documents/R/R_Projects/Distill_Blog/data/ehr_poc2.xlsx",
    sheet =
        "Sheet1",
    na = "MISSING")

## Add 'Age' Column - Age of Claim
ehr_poc1$today <- as.Date(ehr_poc1$today, "%yyyy-%mm-%dd", tz = "EST")
ehr_poc1$dos <- as.Date(ehr_poc1$dos, "%yyyy-%mm-%dd", tz = "EST")

ehr_poc1 <- ehr_poc1 %>%
    mutate(age = days(today) - days(dos))

ehr_poc1$age <- as.numeric(ehr_poc1$age, "hours")

ehr_poc1 <- ehr_poc1 %>%
    mutate(age = age / 24)

## Convert 'Billed' Column to Date Type
ehr_poc1$bill <- as.Date(ehr_poc1$bill, "%yyyy-%mm-%dd", tz = "EST")

## Add 'Bucket' Column to assign an Aging Bucket to each claim
ehr_poc1 <- ehr_poc1 %>%
    mutate(bucket = case_when(
        ehr_poc1$age < 31 ~ "0-30",
        ehr_poc1$age >= 31 & ehr_poc1$age < 61 ~ "31-60",
        ehr_poc1$age >= 61 & ehr_poc1$age < 91 ~ "61-90",
        ehr_poc1$age >= 91 & ehr_poc1$age < 121 ~ "91-120",
        ehr_poc1$age >= 121 & ehr_poc1$age < 151 ~ "121-150",
        ehr_poc1$age >= 151 & ehr_poc1$age < 181 ~ "151-180",
        ehr_poc1$age >= 181 ~ "181+",
        TRUE ~ "Other"
    ))

## Add 'Review' Column to assign Claims to Responsible Party
ehr_poc1 <- ehr_poc1 %>%
    mutate(review = case_when(
        ehr_poc1$stat == "Unsigned" ~ "Client",
        ehr_poc1$stat == "Charges" ~ "Client",
        ehr_poc1$stat == "Location" ~ "Client",
        ehr_poc1$stat == "Refund" ~ "Client",
        ehr_poc1$stat == "Credit" ~ "Client",
        ehr_poc1$stat == "Complete" ~ "None",
        ehr_poc1$stat == "Billed" ~ "Billing",
        ehr_poc1$stat == "New" ~ "Billing",
        ehr_poc1$stat == "Ready" ~ "Billing",
        ehr_poc1$stat == "Rejection" ~ "Billing",
        ehr_poc1$stat == "Denial" ~ "Aging",
        ehr_poc1$stat == "Appeal" ~ "Aging",
        TRUE ~ "Missing Status"
    ))

## Add 'stat2' Column to group Incomplete Statuses
ehr_poc1 <- ehr_poc1 %>%
    mutate(stat2 = case_when(
        ehr_poc1$stat == "Unsigned" ~ "Incomplete",
        ehr_poc1$stat == "Charges" ~ "Incomplete",
        ehr_poc1$stat == "Location" ~ "Incomplete",
        ehr_poc1$stat == "Refund" ~ "Review",
        ehr_poc1$stat == "Credit" ~ "Review",
        ehr_poc1$stat == "Complete" ~ "Complete",
        ehr_poc1$stat == "Billed" ~ "Billed",
        ehr_poc1$stat == "New" ~ "New",
        ehr_poc1$stat == "Ready" ~ "Ready",
        ehr_poc1$stat == "Rejection" ~ "Rejection",
        ehr_poc1$stat == "Denial" ~ "Denial",
        ehr_poc1$stat == "Appeal" ~ "Appeal",
        TRUE ~ "Missing Status"
    ))

## Create the Crosstalk 'SharedData' dataframe
ehr_cross <- SharedData$new(ehr_poc1)
```

```{css css-special}
/* Optional: embed custom fonts here with `@import`          */
/* This must remain at the top of this file.                 */
@import url('https://fonts.googleapis.com/css?family=Karla:400,700');

/* Styles for the table */
.rcm-tbl {
  font-size: 14px;
  line-height: 14px;
  font-family: Karla, "Helvetica Neue", Helvetica, Arial, sans-serif;
}

.rcm-tbl a {
  color: inherit;
}

/* Styles for the column headers */
.col-header {
  border-bottom: 2px solid #555;
  font-size: 12px;
  font-weight: 700;
  text-transform: uppercase;
  font-family: Karla, "Helvetica Neue", Helvetica, Arial, sans-serif;
}

.col-header:hover {
  background-color: #eee;
}

.col-header[aria-sort="ascending"] {
  box-shadow: inset 0 3px 0 0 rgba(0, 0, 0, 0.6) !important;
}

.col-header[aria-sort="descending"] {
  box-shadow: inset 0 -3px 0 0 rgba(0, 0, 0, 0.6) !important;
}

.col-header {
  transition: box-shadow 0.3s cubic-bezier(0.175, 0.885, 0.32, 1.275);
}

.col-footer {
  border-bottom: 2px solid #555;
  font-size: 12px;
  font-weight: 700;
  text-transform: uppercase;
  font-family: Karla, "Helvetica Neue", Helvetica, Arial, sans-serif;
}

/* Styles for the status badges */
.tag {
  display: inline-block;
  padding: 2px 12px;
  border-radius: 15px;
  font-weight: 600;
  font-size: 10px;
}

.status-billed {
  background: hsl(116, 60%, 90%);
  color: hsl(116, 30%, 25%);
}

.status-ready {
  background: hsl(116, 60%, 90%);
  color: hsl(116, 30%, 25%);
}

.status-new {
  background: hsl(116, 60%, 90%);
  color: hsl(116, 30%, 25%);
}

.status-complete {
  background: hsl(350, 70%, 90%);
  color: hsl(350, 45%, 30%);
}

.status-credit {
  background: hsl(350, 70%, 90%);
  color: hsl(350, 45%, 30%);
}

.status-refund {
  background: hsl(350, 70%, 90%);
  color: hsl(350, 45%, 30%);
}

.status-charges {
  background: hsl(0, 100%, 50%);
  color: hsl(230, 45%, 30%);
}

.status-denial {
  background: hsl(230, 70%, 90%);
  color: hsl(230, 45%, 30%);
}

.status-appeal {
  background: hsl(230, 70%, 90%);
  color: hsl(230, 45%, 30%);
}

.status-location {
  background: hsl(230, 70%, 90%);
  color: hsl(230, 45%, 30%);
}

.status-rejection {
  background: hsl(230, 70%, 90%);
  color: hsl(230, 45%, 30%);
}

.status-unsigned {
  background: hsl(230, 70%, 90%);
  color: hsl(230, 45%, 30%);
}
```


<script>
window.FlexDashboardComponents.push({

  type: 'custom',

  find: function(container) {
    if (container.find('span.value-summarywidget-output').length)
      return container;
    else
      return $();
  },

  flex: function(fillPage) {
    return false;
  },

  layout: function(title, container, element, fillPage) {

    // alias variables
    var chartTitle = title;
    var valueBox = element;

    // add value-box class to container
    container.addClass('value-box');

    // value paragraph
    var value = $('<p class="value"></p>');

    // if we have shiny-text-output then just move it in
    var valueOutputSpan = [];
    var shinyOutput = valueBox.find('.shiny-valuebox-output').detach();
    var summaryOutput = valueBox.find('.summarywidget').detach();
    
    if (shinyOutput.length) {
      valueBox.children().remove();
      shinyOutput.html('&mdash;');
      value.append(shinyOutput);
    }
    
    if (summaryOutput.length) {
      value.append(summaryOutput);
      valueOutputSpan = valueBox.find('span.value-summarywidget-output')
    }

    // caption
    var caption = $('<p class="caption"></p>');
    caption.append(chartTitle);

    // build inner div for value box and add it
    var inner = $('<div class="inner"></div>');
    inner.append(value);
    inner.append(caption);
    valueBox.append(inner);

    // add icon if specified
    var icon = $('<div class="icon"><i></i></div>');
    valueBox.append(icon);
    function setIcon(chartIcon) {
      var iconLib = '';
      var iconSplit = chartIcon.split(' ');
      if (iconSplit.length > 1) {
        iconLib = iconSplit[0];
        chartIcon = iconSplit.slice(1).join(' ');
      } else {
        var components = chartIcon.split('-');
        if (components.length > 1)
          iconLib = components[0];
      }
      icon.children('i').attr('class', iconLib + ' ' + chartIcon);
    }
    var chartIcon = valueBox.attr('data-icon');
    if (chartIcon)
      setIcon(chartIcon);

    // set color based on data-background if necessary
    var dataBackground = valueBox.attr('data-background');
    if (dataBackground)
      valueBox.css('background-color', bgColor);
    else {
      // default to bg-primary if no other background is specified
      if (!valueBox.hasClass('bg-primary') &&
          !valueBox.hasClass('bg-info') &&
          !valueBox.hasClass('bg-warning') &&
          !valueBox.hasClass('bg-success') &&
          !valueBox.hasClass('bg-danger')) {
        valueBox.addClass('bg-primary');
      }
    }

    // handle data attributes in valueOutputSpan
    function handleValueOutput(valueOutput) {

      // caption
      var dataCaption = valueOutput.attr('data-caption');
      if (dataCaption)
        caption.html(dataCaption);

      // icon
      var dataIcon = valueOutput.attr('data-icon');
      if (dataIcon)
        setIcon(dataIcon);

      // color
      var dataColor = valueOutput.attr('data-color');
      if (dataColor) {
        if (dataColor.indexOf('bg-') === 0) {
          valueBox.css('background-color', '');
          if (!valueBox.hasClass(dataColor)) {
             valueBox.removeClass('bg-primary bg-info bg-warning bg-danger bg-success');
             valueBox.addClass(dataColor);
          }
        } else {
          valueBox.removeClass('bg-primary bg-info bg-warning bg-danger bg-success');
          valueBox.css('background-color', dataColor);
        }
      }

      // url
      var dataHref = valueOutput.attr('data-href');
      if (dataHref) {
        valueBox.addClass('linked-value');
        valueBox.off('click.value-box');
        valueBox.on('click.value-box', function(e) {
          window.FlexDashboardUtils.showLinkedValue(dataHref);
        });
      }
    }

    // check for a valueOutputSpan
    if (valueOutputSpan.length > 0) {
      handleValueOutput(valueOutputSpan);
    }

    // if we have a shinyOutput then bind a listener to handle
    // new valueOutputSpan values
    shinyOutput.on('shiny:value',
      function(event) {
        var element = $(event.target);
        setTimeout(function() {
          var valueOutputSpan = element.find('span.value-output');
          if (valueOutputSpan.length > 0)
            handleValueOutput(valueOutputSpan);
        }, 10);
      }
    );
  }
});
</script>

Sidebar {.sidebar}
=====================================
<left>

```{r}
    filter_checkbox("stat", "Status", ehr_cross, ~stat)
    filter_select(
            "prov", 
            "Provider", 
            ehr_cross,
            ~prov, 
            multiple = TRUE)
    filter_select(
            "loc", 
            "Location", 
            ehr_cross,
            ~loc, 
            multiple = TRUE)
    filter_select(
            "bucket", 
            "Aging Bucket", 
            ehr_cross,
            ~bucket, 
            multiple = TRUE)
    filter_select(
            "instype", 
            "Aging Class", 
            ehr_cross,
            ~instype, 
            multiple = TRUE)
```
</left>

# Data View

Row {data-width=350}
-----------------------------------------------------------------------

### Encounters Selected

```{r}
valueBoxSummaryWidget(
  summarywidget(
    ehr_cross,
    statistic = 'count',
    column = 'enc',
    digits = 0
  ),
  color = "#E5E5E5"
)
```

### Total Balance

```{r}
valueBoxSummaryWidget(
  summarywidget(
    ehr_cross,
    statistic = 'sum',
    column = 'bal',
    digits = 2
  ),
  color = "#E5E5E5"
)
```

### Average Balance

```{r}
valueBoxSummaryWidget(
  summarywidget(
    ehr_cross,
    statistic = 'mean',
    column = 'bal',
    digits = 2
  ),
  color = "#E5E5E5"
)
```

### Average Age of Encounters

```{r}
valueBoxSummaryWidget(
  summarywidget(
    ehr_cross,
    statistic = 'mean',
    column = 'age',
    digits = 0
  ),
  color = "#E5E5E5"
)
```

### Average Days to Untimely

```{r}
valueBoxSummaryWidget(
  summarywidget(
    ehr_cross,
    statistic = 'mean',
    column = 'timcount',
    digits = 0
  ),
  color = "#E5E5E5"
)
```

Row
-----------------------------------------------------------------------

### 

```{r ehrtable, echo=FALSE, message=FALSE, warning=FALSE}
  div(
class = "rcm-tbl",
## Interactive Billing Reactable
reactable(
    ehr_cross,
    selection = "multiple",
    onClick = "select",
    pagination = TRUE,
    bordered = TRUE,
    highlight = TRUE,
    filterable = FALSE,
    searchable = FALSE,
    compact =TRUE,
    outlined = TRUE,
    striped = FALSE,
    wrap = TRUE,
    paginationType = "jump",
    showPageSizeOptions = TRUE,
    defaultPageSize = 15,
  defaultSorted = list(
      dos = "desc",
      bal = "asc"),
  defaultColDef = colDef(
    class = "rcm-tbl",
    footerStyle = list(fontWeight = "bold"),
    headerClass = "col-header",
    footerClass = "col-footer",
    align = "left",
    vAlign = "center"),
  columns = list(
      enc = colDef(
          name = "Encounter",
          cell = function(value, index) {
        type <- ehr_poc1$type[index]
        type <- if (!is.na(type)) type else "Unknown"
        div(
          div(style = list(fontWeight = 600), value),
          div(style = list(fontSize = 12), type)
        )
      }
          ),
      type = colDef(
          name = "Type",
          show = FALSE
          ),
      pt = colDef(
          name = "Patient"
          ),
      dos = colDef(
          name = "DOS",
          format = colFormat(date = TRUE)
          ),
      prov = colDef(
          name = "Provider",
          na = "MISSING",
          #width = 80
          ),
      loc = colDef(
          name = "Location",
          na = "MISSING",
          #width = 80
          ),
      payer = colDef(
          name = "Payer",
          na = "MISSING",
          #width = 80
          ),
      instype = colDef(
          name = "Class",
          na = "MISSING",
          #width = 80
          ),
      stat = colDef(
          name = "Status",
          cell = 
              function(value) 
                  {class <- paste0("tag status-", tolower(value))
                  div(class = class, value)}
          ),
      bill = colDef(
          name = "Billed",
          format = colFormat(date = TRUE),
          na = "UNBILLED"
          ),
      bal = colDef(
                    style = color_scales(
            ehr_poc1, 
            colors = pal_material(
              "blue-grey", 
              n = 6, 
              alpha = 1.0, 
              reverse = FALSE)(6)),
          name = "Balance",
          #width = 100,
          format = colFormat(
              separators = TRUE,
              digits = 2),
              na = "MISSING",
          footer = JS("function(colInfo) {
        let total = 0
        colInfo.data.forEach(function(row) {
          total += row[colInfo.column.id]
        })
        return '$' + total.toFixed(2)
      }")
      ),
      today = colDef(
          name = "Today",
          format = colFormat(date = TRUE),
          show = FALSE
          ),
      note = colDef(
          name = "Note",
          format = colFormat(date = TRUE),
          show = FALSE
          ),
      age = colDef(
          name = "Age",
          style = color_scales(
            ehr_poc1, 
            colors = pal_material(
              "blue-grey", 
              n = 6, 
              alpha = 1.0, 
              reverse = FALSE)(6)),
          #width = 50,
          na = "MISSING"
          ),
      bucket = colDef(
          name = "Aging Bucket",
          #width = 60,
          na = "MISSING"
          ),
      timfilelim = colDef(
          name = "Timely Filing Limit",
          show = FALSE,
          # width = 60,
          na = "MISSING"
          ),
      timfildate = colDef(
          name = "Timely Filing Deadline",
          show = FALSE,
          # width = 60,
          na = "MISSING"
          ),
      timcount = colDef(
          name = "Days to Untimely",
          style = color_scales(
            ehr_poc1, 
            colors = pal_material(
              "blue-grey", 
              n = 6, 
              alpha = 1.0, 
              reverse = TRUE)(6)),
          #width = 60,
          na = "NA"
          ),
      stat2 = colDef(
          name = "Status",
          show = FALSE,
          # width = 60,
          na = "MISSING"
          ),
      review = colDef(
          name = "Review",
          show = TRUE,
          # width = 60,
          na = "MISSING"
          )
    )
  )
)
# )
```
